\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning, Reachability Analysis, and Network Flow

### 2024-12-09 response.tex

%% Sets page size and margins
\usepackage[a4paper,top=2.5cm,bottom=2cm,left=1.7cm,right=1.7cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
% \usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{indentfirst}
\usepackage{graphicx}
% \usepackage{subfigure}
\usepackage{float}
\usepackage{threeparttable} 
\usepackage{multirow}
\usepackage{url}
\usepackage{xcolor}
\pagenumbering{arabic}

\usepackage[most]{tcolorbox}
\newcommand{\rrtstar}{$\texttt{RRT}^\texttt{*}$}
\newcommand{\SubItem}[1]{
    {\setlength\itemindent{15pt} \item[-] #1}
}

\newtheorem{constraint}{ADMM constraint}
\newtheorem{example}{Example}
\newcommand{\re}{\tcblower \underline{\textbf{Response:}}}
\newcommand{\rv}{{\Large{\underline{\textbf{Revision:}}}}\quad}
\usepackage[export]{adjustbox} 
\usepackage[capitalise]{cleveref}
\usepackage{xcolor}
\newcommand{\new}[1]{\textcolor{blue}{#1}}
\newcommand{\news}{\color{blue}}
\graphicspath{{Figs/}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Rewiewer 1
\newpage
\section{Response to reviewer 1}

%%%%%%%%%%%%% Comment 1.1
\begin{cmt*}{}{}

	This paper proposes a multi-agent mobile robot planning algorithm that
	is robust agains attackers that would compromise the agents by
	directing them to unsafe regions. This is achieved by incorporating 1)
	co-observation constraints so that the agents could watch over each
	other, 2) reachability constraints so that the region the agents could
	potentially enter does no overlap with unsafe regions, and 3) sub-team
	planning algorithm to improve robustness by adding more number of
	agents.

	The proposed method is interesting, but I think the writing must be
	improved significantly to secure the clarity, and there are a lot of
	grammar mistakes that need to be fixed. To me, it appears that the
	draft may have been prepared somewhat hastily, which is not considerate
	of the reviewers' time.
	\tcblower
	\underline{\textbf{Response:}} We are grateful for your thoughtful comments and for expressing interest in our proposed method. We sincerely apologize for the grammatical mistakes in the initial submission and acknowledge the importance of presenting our work with clarity and professionalism. In the revised version, we have been extra careful to address all grammar issues and have implemented thorough proofreading to minimize similar mistakes in future submissions. We greatly appreciate your patience and constructive feedback, which have been invaluable in improving the quality of our manuscript.

\end{cmt*}
\vspace{0.1cm}
%%%%%%%%%%%%% Comment 1.0
\begin{cmt}{}{}        %% use * when do not need enumerate
	It seems like Example 1 is introduced as an example to help
	readers understand the formulation (1) in details. However, it is still
	vague, and it doesn't easily connect to Figure 3b.
	\tcblower
	\underline{\textbf{Response:}} Example 1 has been revised to improve clarity, with additional illustrative content and an updated figure added to better showcase the example application and its relevance to the proposed approach.
\end{cmt}
\rv
\begin{example}\label{example:map_exploration}
\new{Robots are tasked with navigating an unknown task space to collecte sensory data to reconstruct a field (as illustrated in~\cref{fig:illustration}). The task space is modeled as a grid, where each grid point has an associated value tracked by a Kalman Filter (KF) [28]. The KF estimates uncertainty at each point through its covariance $P_j$ updated based on the measurements taken by robots along the trajectory $\vq$. Measurement quality, modeled by a Gaussian radial basis function, decreases with distance from the robot. The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty in reconstructing the field (detailed in [6]). }
\end{example}
\setcounter{figure}{1}
\begin{figure}[H]
	\centering
	\subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.4\linewidth,valign=c]{illustration figure_1}} 
	\subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.4\linewidth,valign=c]{SecurityBreak_v2}}
	% \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.4	\linewidth]{Grid_world}}
	\caption{\new{(2a) Illustration of a 3 robot map exploration task case. (2b) The unsecured trajectory design optimized for a map exploration task. Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
\end{figure}
{\news In the absence of further security requirements, the robots are expected to spread out and follow a boustrophedon pattern, efficiently exploring as much of the task space as possible (as illustrated in Fig.2b). This exploration strategy optimizes coverage and minimizes reconstruction uncertainty across the field. }

%%%%%%%%%%%%% Comment 1.2
\begin{cmt}{}{}
	Personally, I think to much space is dedicated to the details of how
	reachability constraints are implemented in the ADMM formulation (Sec.
	D, E, F, G, H). Although they are important details, I think this part
	can be condensed more, and some of the details can be deferred to the
	Appendix, so that some space can be dedicated more to improve the
	clarity of the other sections.
	\tcblower
	\underline{\textbf{Response:}} As suggested, we have condensed this section and moved the “Transformation to Canonical Frame” part into the appendix to streamline the main text and improve readability. We believe that the remaining details on the implementation of the reachability constraints are essential and provide critical context for understanding the proposed method. We appreciate your suggestion, which has helped us enhance the balance and clarity of the manuscript. 
\end{cmt}
\rv
\renewcommand\thesubsection{D}
 \subsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
{\news	\newcommand{\oFE}{o}
 To use the definition of reachability ellipsoid from the section above as computational constraints for ADMM, we first apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center $\oFE = \frac{1}{2}(q_1+q_2)$, and the first axis of $\cF_\cE$ is aligned with the foci (see Fig.3a for an illustration). 
From this definition, a unit vector along the first axis of the ellipsoid in the frames $\cF$ and $\cF_\cE$ is given by $\nu_\cF = \frac{q_2-q_1}{\norm{q_2-q_1}}$ and $\nu_\cE =[1,0,0]^T$, respectively.
The full transformation from coordinates $q^\cE\in\cF$ to $q\in\cF$, and its inverse, are then parametrized by a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$ as (we drop the subscript and superscript from $R^\cF_\cE$ and $o^\cF_\cE$ to simplify the notation):
\setcounter{equation}{9}
\begin{equation}\label{eq:transformations}
  q=R\Eframe{q}+\oFE,\quad
  \Eframe{q}=R\transpose(q-\oFE).
\end{equation}
where the rotation matrix $R=H(\nu_\cF(q_1,q_2),\nu_\cE)$ is a \emph{Householder rotation} $H$ (a differentiable linear transformation describing the minimal rotation between the two vectors, see Appendix B for details).  To simplify the notation, in the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. More details on (10) are given in Appendix A.
  Reachability constraints are formulated with respect to different types of forbidden regions a point, a plane, a segment, and a convex polygon.}
\renewcommand\thesubsection{F}
\subsection{Plane-ellipsoid reachability constraint}\label{sec:ellipsoide-plane}
\new{For a hyperplane shaped forbidden region $\mathcal{L}(q) = \{q\in\mathbb{R}^m: \vn\transpose q = d\}$ (Fig.3c), the reachability constraint is $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$. When transformed into the canonical frame, the hyperplane can be written as $\Eframe \cL(\Eframe{q}) = \{  \Eframe{q}\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe{q} = d_{\cE}\}$, with $\vn_\cE = H(q_1,q_2)\vn, \quad d_\cE =-\vn\transpose o + d$.}
%%
\renewcommand\thesubsection{G}
\def\sZ{\mathcal{Z}}
\subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint}
{\news  
The reachability constraints for a convex polygon is treated as a union of reachability constraints for aeach indivisual segments that define the hyperplane. We define
\setcounter{constraint}{3}
\setcounter{equation}{29}
\begin{constraint}[Convex-polygon-ellipsoid reachability constraint]\label{constraint:polygon-ellipsoid}
\begin{align}
D(\vq) &= \bmat{D_{seg1}(\vq)\\D_{seg2}(\vq)\\ \vdots} \label{eq:region_ellipsoid_constraint}\\
  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
   \Pi_\sZ(\vz) & = 0, 
\end{align}
\end{constraint}
where $D_{seg}$ are the constraint functions for all line segments used to define the convex polygon region. 
For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:
\begin{equation}
\bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), \quad \vn_\cE\transpose \Eframe q = d_{\cE}.
\end{equation}
When the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e. red region in Fig. 3d), the constraint is a plane-ellipse constraint in Section II-F. Otherwise (i.e. brown region in Fig. 3d), the constraint is a point-ellipse constraint in Section II-F.

\begin{constraint}[Line-segment-ellipsoid reachability constraint]
\begin{align}
D_{seg}(\vq) &=  \begin{cases}
D_{p_{1}}(\vq) & (\Eframe{p_1}-\Eframe{p_2})\transpose (\Eframe{p_{\cL}}-\Eframe{p_2})<0\\
D_{p_{2}}(\vq) & (\Eframe{p_2}-\Eframe{p_1})\transpose (\Eframe{p_{\cL}} -\Eframe{p_1})<0\\
D_\Eframe{p_{\cL}}(\vq) & \textrm{otherwise}
\end{cases} \label{eq:segment_ellipsoid_constraint}\\
  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D_{seg}(\vq)} = 0 \},\\
   \Pi_\sZ(\vz) & = 0, 
\end{align}
\end{constraint}
where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function (11) respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint (22). with respect to frame $\Eframe {\cL}$.
This constraint needs to be supplemented with a convex obstacle constraint for the polygon (i.e. keep foci waypoints outside the region, introduced in [6]) to prevent cases where the ellipse is a subset of the region.
}

\vspace{0.2cm}
%%%%%%%%%%%%% Comment 1.3
\begin{cmt}{}{}
	The word “checkpoint” appears abruptly in page 6 without concrete
	definition, although it seems like it is an important component of the
	formulation, and an important design choice for the results. For
	example, in the way Figure 3 is presented, I don't get a good idea why
	the checkpoint location is there in (c). 
	\re 
	\noindent
 For the feedback reguarding the term "checkpoint", the original intent of “checkpoint” in Section 2 was to illustrate the limitations of the method proposed, specifically to show that even if APMAPF yields a valid solution, transforming this solution to a continuous domain may still need additional security measure to guarantee security. To address the concern, we have replaced the term “checkpoints” with “key locations” in Section 2 to avoid confusion. Additionally, we have added a formal definition of “checkpoints” and the “checkpoint graph” later in Section 3 to provide a clear and precise explanation of these concepts. These updates ensure that the term is used consistently and that its role in the methodology is explicitly defined. 
\end{cmt}
\rv
\renewcommand\thesubsection{H}
\subsection{Secured planning results and limitation}\label{sec:ADMM-simulation}
We employ the \new{attack-proof MAPF(APMAPF)} solver [2] on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.4a). This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with an additional task function targeting the map exploration task. Co-observation schedules are set up using the APMAPF algorithm for two forbidden regions. Reachability constraints are added to ensure an empty intersection between all robots' reachability regions during co-observations and the forbidden regions. {\news It is important to emphasize that an APMAPF solution does not guarantee existence, nor does it ensure a successful transition to the continuous configuration space. In this case, while an APMAPF solution may be found, the secured, attack-proof solution becomes infeasible in the continuous setting because the robots' mobility is no longer restricted to adjacent grids. Additional security measures, such as stationary security cameras or surveillance robots, need to be incorporated. For instance, in this scenario, we deploy a security camera as additional security measure to observe agent 3 at time $8$ to ensure security.}

The simulation result, shown in Fig.4b, displays reachability regions as black ellipsoids, demonstrating empty intersections with Zones 2 and 3. Explicit constraints between reachability regions and obstacles are not activated, assuming basic obstacle avoidance capabilities in robots. The intersections between obstacles and ellipsoids, as observed between agent 3 and Zone 1, are deemed tolerable. All constraints are satisfied, and agents have effectively spread across the map for optimal exploration tasks.

1) Limitations:
Our solution demonstrates the potential of planning with reachability and co-observation to enhance the security of multi-agent systems. {\news However, two primary challenges need to be addressed. Firstly, achieving a co-observation and reachability-secured plan is not always feasible, particularly when obstacles or restricted regions separate the robots, preventing them from establishing co-observation schedules or finding reachability-secured paths. For example, agent 3 in~Fig.4b requires additional security measures to create secured reachability areas. Secondly, security requirements can impact overall system performance, as illustrated by the comparison between~Fig.2b and Fig.4b. The introduction of security constraints resulted in the top left corner remaining unexplored by any robots. This trade-off between security and system performance is particularly significant as system performance is a key factor in the decision of multi-agent system deployments. These challenges are further addressed in Section III, ensuring the effective integration of reachability and co-observation in securing multi-agent systems.}

@@

\vspace{0.3cm}

\begin{cmt}{}{}
	Similarly, how the
	trajectories are broken down to multiple ellipsoid components are not
	clear, is it a design choice to make the constraints less conservative
	than setting a single ellipsoid with the start and goal point?
	\re 
	The reachability ellipsoids are designed to work in conjunction with the co-observation technique. Instead of using a single ellipsoid defined by the start and goal points, the trajectory is divided into smaller ellipsoids based on co-observation times. This approach ensures that the constraints are aligned with the co-observation schedule, reducing conservativeness while maintaining security guarantees. We also make modification to Definition 4 (Remark 1 in the original manuscript) to make this more clear.
\end{cmt}
\rv
{\news \setcounter{definition}{3}
 \begin{definition}\label{rmk:revised-security}
	A multi-robot trajectory is secured against plan-deviation attacks if there exists a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
\end{definition}}

\vspace{0.3cm}
\begin{cmt}{}{}
	Similarly, in page 7, “key locations” and “checkpoint graph” are
	mentioned without clear explanations what they are.
	\re  
	In Section III, we add additional definition to 'checkpoint' and 'checkpoint graph'
\end{cmt}
\rv

### 2024-12-09 paper.tex
finish response reviewer 1

\section{Secured Multi-robot trajectory planning}\label{sec:ADMM-planning}
We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions. {\news We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$, where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space, $T$ is the time horizon. For a total of $n_p$ robots, trajectories can be represented as an aggregated vector $\vq = \stack(\vq_1,\dots,\vq_{n_p})\in \real{m n_p\times T}$, where $\stack(\cdot)$ denotes the vertical stacking operation. }
\new{The overall goal is to minimize or maximize an objective function $\varPhi(\vq):\real{n m T} \to \real{}$ under a set of nonlinear constraints described by a set $\Omega$, which is given by the intersection of spatio-temporal sets given by traditional path planning constraints and the security constraints (co-observation schedule, reachability analysis).} Formally:
\begin{equation}\label{eq:general-problem}
	\begin{split}
		\min/\max & \quad \varPhi(\vq)\\
		\textrm{subject to} &\quad \vq \in \Omega.
	\end{split}
\end{equation}

To give a concrete example of the cost $\varPhi$ and the set $\Omega$, we introduce a representative application that will be used for all the simulations throughout the paper.

\begin{example}\label{example:map_exploration}
\new{Robots are tasked to navigate an unknown task space, collecting sensory data to reconstruct a field (see~\cref{fig:illustration}). The space is modeled as grid points, each with an associated value. The goal is to find paths that minimize uncertainty in reconstructing the field. Each grid point $j$ is associated with a Kalman Filter (KF) \cite{anderson2012optimal} to track uncertainty through its covariance $P_j$, updated based on the measurements taken by robots along the trajectory $\vq$, where measurement quality, modeled by a Gaussian radial basis function, is higher near the robot. The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty (detailed in \cite{yang2020multi}).}

% Robots are tasked to navigate, collecting sensory data of an unknown task space to map a slowly-varying field, denoted as $\vx$, (see Figure~\ref{fig:SecurityBreak}). The map comprises points of interest arranged on a grid, each associated with a slowly-changing value. Our goal is to find paths that minimize uncertainty and effectively reconstruct the field. We associate a Kalman Filter (KF)~(cf. \cite{anderson2012optimal}) to each point $j$, and use it to track the uncertainty through its estimated covariance $P_j$. The updates of the filters are based on measurements from the robot centered at $q$, and we use a Gaussian radial basis function  modeling spatially-varying measurement quality. The optimization objective $\varPhi(\vq)$ is written as the maximum uncertainty $\max_j P_{j}$ (detailed formulation can be found in \cite{yang2020multi}).
\end{example}
\begin{figure}
  \centering
  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth]{illustration figure_1}} 
  \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
  \caption{\new{(a) Grid world example of a task planned in an $8 \times 8$ grid world. Blue grids are obstacles, orange and green grids are forbidden regions.}}
\end{figure}

@@

To incorporate the security against malicious deviations (through co-observation and reachability analysis) as constraints in the optimal trajectory planning problem, we define the security as:
\begin{definition}\label{def:secured-plan}
  A multi-robot trajectory plan is \new{secured against} plan-deviation attacks if it \new{ensures} that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots. 
\end{definition}

@@

  \begin{proposition}\label{prop:dpi_ne_dt}
    The differential of the projection function $\pi^\cE_{\vn \cE}(\vq)$ with respect to the foci $q_1$ and $q_2$ is given by:
    \begin{equation}
      \partial_q \pi^\cE_{\vn \cE}(q) = \begin{cases}
        \partial_q p^\cE_{t1}-\partial_q p^\cE_{\cL} &  d_\cE \in [0, d_{\cE t}], \\
        \partial_q p^\cE_{t2}-\partial_q p^\cE_{\cL} &  d \in [- d_{\cE t},0), \\
        {0} & otherwise.
      \end{cases}
    \end{equation}
    where
    \begin{multline}
      \partial_q p_\cL =   (-\frac{d_{\cE t} n\transpose \partial_q o -2d_\cE \partial_q d_{\cE t}}{d_{\cE t}^3} )Q^{-1}n_\cE \\
      + \frac{d_\cE\partial_b Q^{-1} n_\cE \partial_q b -  2d_\cE Q^{-1}H[n]_\times U}{d_{\cE t}^2},
    \end{multline}
    \begin{equation}
      \partial_q p_{1} =  -\frac{Q^{-1}n_\cE \partial_q d_{\cE t} }{d_{\cE t}^2} 
      + \frac{\partial_b Q^{-1}n_\cE \partial_q b -  2Q^{-1}H[n]_\times U }{d_{\cE t}}.
    \end{equation}
  \end{proposition}
  \begin{proof}
  See \cref{proof:dpi_ne_dt}.
  \end{proof}
 The differential of (\ref{eq:plane_ellipsoid_constraint}) can be written as:
  \begin{equation}
    \partial_q {D_{\vn\cE}} = -2 H \cross{\Eframe \Pi_{\vn \cE}}  M + H^{-1}\partial_q \Eframe \Pi_{\vn \cE}.
  \end{equation}
\subsection{Line-segment-ellipse reachability constraint}\label{chapter:ellipse to segment}
{\news As an intermediate step to consider polygon-shaped forbidden regions, the reachability constraint for hyperplane segments is studied.
For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:}
\begin{equation}
\bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), \quad \vn_\cE\transpose \Eframe q = d_{\cE}.
\end{equation}
When the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e. red region in \cref{fig:Ellipse-to-safezone}), the constraint is a plane-ellipse constraint in \cref{sec:ellipsoide-plane}. Otherwise (i.e. brown region in \cref{fig:Ellipse-to-safezone}), the constraint is a point-ellipse constraint in \cref{sec:ellipsoid-point}.

\begin{constraint}[Line-segment-ellipsoid reachability constraint]
\begin{align}
D(\vq) &=  \begin{cases}
D_{p_{1}}(\vq) & (\Eframe{p_1}-\Eframe{p_2})\transpose (\Eframe{p_{\cL}}-\Eframe{p_2})<0\\
D_{p_{2}}(\vq) & (\Eframe{p_2}-\Eframe{p_1})\transpose (\Eframe{p_{\cL}} -\Eframe{p_1})<0\\
D_\Eframe{p_{\cL}}(\vq) & \textrm{otherwise}
\end{cases} \label{eq:segment_ellipsoid_constraint}\\
  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
   \Pi_\sZ(\vz) & = 0, 
\end{align}
\end{constraint}
where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function~\eqref{eq:point_ellipsoid_constraint} with respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint~\eqref{eq:plane_ellipsoid_constraint}. with respect to frame $\Eframe {\cL}$.

\subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint} 
For reachability constraints with respect to a convex polygon, the first step is to keep all segments that define the hyperplane outside the reachability ellipsoid. Similar to \eqref{equ:ProjectPoint}, we define
\begin{constraint}[Convex-polygon-ellipsoid reachability constraint]\label{constraint:polygon-ellipsoid}
\begin{align}
D(\vq) &= \bmat{D_{seg1}(\vq)\\D_{seg2}(\vq)\\ \vdots} \label{eq:region_ellipsoid_constraint}\\
  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
   \Pi_\sZ(\vz) & = 0, 
\end{align}
\end{constraint}
where $D_{seg}$ are the constraint functions for all line segments used to define the convex polygon region. This constraint needs to be supplemented with a convex obstacle constraint for the polygon (i.e. keep foci waypoints outside the region, introduced in \cite{yang2020multi}) to prevent cases where the ellipse is a subset of the region.

\subsection{Secured planning results and limitation}\label{sec:ADMM-simulation}

>>>>

\section{Secured Multi-robot trajectory planning}\label{sec:ADMM-planning}
We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions. {\news We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$, where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space, $T$ is the time horizon. For a total of $n_p$ robots, trajectories can be represented as an aggregated vector $\vq = \stack(\vq_1,\dots,\vq_{n_p})\in \real{m n_p\times T}$, where $\stack(\cdot)$ denotes the vertical stacking operation. }
\new{The overall goal is to minimize or maximize an objective function $\varPhi(\vq):\real{n m T} \to \real{}$ under a set of nonlinear constraints described by a set $\Omega$, which is given by the intersection of spatio-temporal sets given by traditional path planning constraints and the security constraints (co-observation schedule, reachability analysis).} Formally:
\begin{equation}\label{eq:general-problem}
	\begin{split}
		\min/\max & \quad \varPhi(\vq)\\
		\textrm{subject to} &\quad \vq \in \Omega.
	\end{split}
\end{equation}
To give a concrete example of the cost $\varPhi$ and the set $\Omega$, we introduce a representative application that will be used for all the simulations throughout the paper.

\begin{example}\label{example:map_exploration}
\new{Robots are tasked with navigating an unknown task space to collecte sensory data to reconstruct a field (as illustrated in~\cref{fig:illustration}). The task space is modeled as a grid, where each grid point has an associated value tracked by a Kalman Filter (KF) \cite{anderson2012optimal}. The KF estimates uncertainty at each point through its covariance $P_j$ updated based on the measurements taken by robots along the trajectory $\vq$. Measurement quality, modeled by a Gaussian radial basis function, decreases with distance from the robot. The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty in reconstructing the field (detailed in \cite{yang2020multi}). }
\end{example}
\begin{figure}
  \centering
  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,valign=c]{illustration figure_1}} 
  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
  % \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
  \caption{\new{(\ref{fig:illustration}) Illustration of a 3 robot map exploration task case. (\ref{fig:SecurityBreak}) The unsecured trajectory design optimized for a map exploration task. Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
\end{figure}

% To give a concrete example of the cost $\varPhi$ and the set $\Omega$, we introduce a representative application that will be used for all the simulations throughout the paper.

% \begin{example}\label{example:map_exploration}
% \new{Robots are tasked to navigate an unknown task space, collecting sensory data to reconstruct a field (see~\cref{fig:illustration}). The space is modeled as grid points, each with an associated value. The goal is to find paths that minimize uncertainty in reconstructing the field. Each grid point $j$ is associated with a Kalman Filter (KF) \cite{anderson2012optimal} to track uncertainty through its covariance $P_j$, updated based on the measurements taken by robots along the trajectory $\vq$, where measurement quality, modeled by a Gaussian radial basis function, is higher near the robot. The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty (detailed in \cite{yang2020multi}).}
% \end{example}
% \begin{figure}
%   \centering
%   \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth]{illustration figure_1}} 
%   \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
%   \caption{\new{(a) Grid world example of a task planned in an $8 \times 8$ grid world. Blue grids are obstacles, orange and green grids are forbidden regions.}}
% \end{figure}

@@

{\news In the absence of further security requirements, the robots are expected to spread out and follow a boustrophedon pattern, efficiently exploring as much of the task space as possible (as illustrated in~\cref{fig:SecurityBreak}). This exploration strategy optimizes coverage and minimizes reconstruction uncertainty across the field. }To incorporate the security against malicious deviations (through co-observation and reachability analysis) as constraints in the optimal trajectory planning problem, we define the security as:
\begin{definition}\label{def:secured-plan}
  A multi-robot trajectory plan is \new{secured against} plan-deviation attacks if it \new{ensures} that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots. 
\end{definition}

@@

  \begin{proposition}\label{prop:dpi_ne_dt}
    The differential of the projection function $\pi^\cE_{\vn \cE}(\vq)$ with respect to the foci $q_1$ and $q_2$ is given by:
    \begin{equation}
      \partial_q \pi^\cE_{\vn \cE}(q) = \begin{cases}
        \partial_q p^\cE_{t1}-\partial_q p^\cE_{\cL} &  d_\cE \in [0, d_{\cE t}], \\
        \partial_q p^\cE_{t2}-\partial_q p^\cE_{\cL} &  d \in [- d_{\cE t},0), \\
        {0} & otherwise.
      \end{cases}
    \end{equation}
    where
    \begin{multline}
      \partial_q p_\cL =   (-\frac{d_{\cE t} n\transpose \partial_q o -2d_\cE \partial_q d_{\cE t}}{d_{\cE t}^3} )Q^{-1}n_\cE \\
      + \frac{d_\cE\partial_b Q^{-1} n_\cE \partial_q b -  2d_\cE Q^{-1}H[n]_\times U}{d_{\cE t}^2},
    \end{multline}
    \begin{equation}
      \partial_q p_{1} =  -\frac{Q^{-1}n_\cE \partial_q d_{\cE t} }{d_{\cE t}^2} 
      + \frac{\partial_b Q^{-1}n_\cE \partial_q b -  2Q^{-1}H[n]_\times U }{d_{\cE t}}.
    \end{equation}
  \end{proposition}
  \begin{proof}
  See \cref{proof:dpi_ne_dt}.
  \end{proof}
 The differential of (\ref{eq:plane_ellipsoid_constraint}) can be written as:
  \begin{equation}
    \partial_q {D_{\vn\cE}} = -2 H \cross{\Eframe \Pi_{\vn \cE}}  M + H^{-1}\partial_q \Eframe \Pi_{\vn \cE}.
  \end{equation}
% \subsection{Line-segment-ellipse reachability constraint}\label{chapter:ellipse to segment}
% {\news As an intermediate step to consider polygon-shaped forbidden regions, the reachability constraint for hyperplane segments is studied.
% For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:}
% \begin{equation}
% \bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), \quad \vn_\cE\transpose \Eframe q = d_{\cE}.
% \end{equation}
% When the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e. red region in \cref{fig:Ellipse-to-safezone}), the constraint is a plane-ellipse constraint in \cref{sec:ellipsoide-plane}. Otherwise (i.e. brown region in \cref{fig:Ellipse-to-safezone}), the constraint is a point-ellipse constraint in \cref{sec:ellipsoid-point}.
